Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed Quasars

### 2020-08-10 manuscript/manuscript.tex
Receive referee report and before sec editing
Git push before sharing to TT

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% my commands
\newcommand{\lcdm}{$\Lambda$CDM}
\newcommand{\hst}{{\it HST}}
\newcommand{\hc}{$H_0$}
\newcommand{\efr}{$R_{\mathrm{eff}}$}
\newcommand{\galfit}{{\sc Galfit}}
\newcommand{\mbh}{$\mathcal M_{\rm BH}$}
\newcommand{\lhost}{$L_{\rm host}$}
\newcommand{\mr}{$Mag_{\rm ~R}$}
\newcommand{\halpha}{H$_{\alpha}$}
\newcommand{\Hb}{H$_{\beta}$}
\newcommand{\sersic}{S\'ersic}
\newcommand{\lenstronomy}{{\sc Lenstronomy}}
\newcommand{\reff}{{$R_{\mathrm{eff}}$}}
\newcommand{\kmsMpc}{km~s$^{\rm -1}$~Mpc$^{\rm -1}$}
\newcommand{\kms}{\ifmmode{\,\rm{km}\, \rm{s}^{-1}}\else{$\,$km$\,$s$^{-1}$}\fi}
\newcommand{\sigstar}{{$\sigma_*$}}
\newcommand{\mstar}{{$M_*$}}
\newcommand{\Mgii}{Mg$_{\rm II}$}
\newcommand{\Civ}{C$_{\rm IV}$}
%\newcommand{\farcs}{\mbox{\ensuremath{.\!\!^{\prime\prime}}}}% fractional arcsecond symbol: 0.''0
\newcommand{\sam}{\texttt{SAM}}
\newcommand{\mbii}{\texttt{MBII}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
\newcommand{\todo}[1]{\textcolor{red}{[{\bf Todo}: #1]}}  
\newcommand{\red}[1]{{ \textcolor{red}{#1}}}
\newcommand{\blue}[1]{{ \textcolor{blue}{#1}}}
\newcommand{\pink}[1]{{\textcolor{magenta}{#1}}}

@@

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[X. Ding et al.]{
Xuheng Ding,$^{1}$\thanks{E-mail: dxh@astro.ucla.edu}
Tommaso Treu,$^{1}$
Simon Birrer,$^{2}$
Adriano Agnello,$^{3}$\newauthor
Dominique Sluse,$^{4}$
Chris Fassnacht,$^{5}$
Matthew W. Auger,$^{6}$
Kenneth C. Wong,$^{7}$ \newauthor
Sherry H. Suyu,$^{8,9,10}$
Takahiro Morishita,$^{11}$
Cristian E. Rusu,$^{12,13,14}$
Aymeric Galan,$^{15}$
\\
\\
% List of institutions
$^{1}$Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{3}$European Southern Observatory, Karl-Schwarzschild-Strasse 2, 85748 Garching, Germany\\
$^{4}$STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium\\
$^{5}$Department of Physics, University of California, Davis, CA 95616, USA\\
$^{6}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
$^{7}$Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
$^{8}$Max-Planck-Institut f{\"u}r Astrophysik, Karl-Schwarzschild-Str.~1, 85748 Garching, Germany\\
$^{9}$Physik-Department, Technische Universit\"at M\"unchen, James-Franck-Stra\ss{}e~1, 85748 Garching, Germany\\
$^{10}$Academia Sinica Institute of Astronomy and Astrophysics (ASIAA), 11F of ASMAB, No.1, Section 4, Roosevelt Road, Taipei 10617, Taiwan\\
$^{11}$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA\\
$^{12}$National Astronomical Observatory of Japan, 2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan\\
$^{13}$Subaru Telescope, National Astronomical Observatory of Japan, 650 N Aohoku Pl, Hilo, HI 96720\\
$^{14}$Department of Physics, University of California, Davis, 1 Shields Avenue, Davis, CA 95616, USA\\
$^{15}$Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique 
F\'ed\'erale de Lausanne (EPFL), Observatoire de Sauverny, 1290 Versoix, 
Switzerland
}

@@

% Abstract of the paper
\begin{abstract}
One of the main challenges in using high redshift active galactic nuclei to study the correlations between the mass of the supermassive Black Hole (\mbh) and the properties of their active host galaxies is instrumental resolution. Strong lensing magnification effectively increases instrumental resolution and thus helps to address this challenge. In this work, we study eight strongly lensed active galactic nuclei (AGN) with deep {\it Hubble Space Telescope} (\hst) imaging, using the lens modelling code \lenstronomy\ to reconstruct the image of the source. Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on stellar population models.  \mbh\ are estimated from broad emission lines using standard methods. Our results are in good agreement with recent work based on non-lensed AGN, providing additional evidence that the correlation evolves over cosmic time.  At the moment, the sample size of lensed AGN is small and thus they provide mostly a consistency check on systematic errors related to resolution for the non-lensed AGN. However, the number of known lensed AGN is expected to increase dramatically in the next few years, through dedicated searches in ground and space based wide field surveys, and they may become a key diagnostic of black hole and galaxy co-evolution. 
\end{abstract}

@@

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
\section{Introduction}
The tight correlations between the masses (\mbh) of supermassive black holes (BHs) and their host galaxies properties including stellar mass (\mstar), stellar velocity dispersion ($\sigma_*$) and luminosity (\lhost), known as scaling relations, are usually considered as a result of their co-evolution ~\citep[e.g.,][]{Mag++98, F+M00, Geb++01b, M+H03, Gul++09,Beifi2012, H+R04, Gra++2011}. Cosmological simulations of structure formation are able to reproduce the local tight relation based on physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or having them share a common gas supply~\citep{Cen2015, Menci2016}. However, it has also been suggested that the correlations arise statistically, without any physical coupling, as a result of stochastic mergers~\citep{Peng2007, Jahnke2011, Hirschmann2010}.

@@

As the samples of AGN grow to increase statistical power, it is very important to make sure that systematics do not dominate the error budget. One of the main potential source of systematics is the finite resolution of \hst\ images. Even with modern techniques, AGN hosts remain barely resolved at \hst\ resolution, and therefore it would be very useful to verify the results at higher resolution. This is the goal of this work.

@@

The sample of lensed AGN is too limited in size to constrain evolution by itself. Therefore, we use it primarily to verify the results of D20.  The D20 sample includes 32 AGN measurements in the redshift range $1.2<z<1.9$. They also collected 59 intermediate redshift (i.e., $0.35<z\lesssim1.2$) AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 local (i.e., $z\lesssim0.007$) measurements~\citep{Bennert++2011, H+R04}. It is worth noting that they are so far the largest \hst\ imaging AGN sample with redshift range up to $z\sim1.9$.

@@

To ensure the consistency of \mbh\ estimates based on different broad lines, we adopt the following set of self-consistent recipes following D20:
\begin{eqnarray}
\label{recipe}
\log \left(\frac{\mathcal M_{\rm BH}}{M_{\odot}}\right)&~=~& a+b \log \left(\frac{ \rm L _{\lambda_{line}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2 \log \left(\frac{\rm FWHM(line)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}
where $\lambda_{\rm line}$ is the reference wavelength of the local continuum luminosities for different emission lines. The following values are adopted:
%
$a$\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
$b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
$\lambda_{\rm line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}~(\AA).
%
The broad line properties of our samples are adopted from the literature, with a few corrections/exceptions. % \citep{Sluse2012, Peng2006, Shen2011}.
The line properties of SDSS1206 have been inferred by~\citet{Shen2011}. However, this system was investigated as a non-lensed AGN and the lensing magnification on the intrinsic continuum luminosity was not considered. We follow~\citet{Birrer2019} and apply the same magnification correction on the $\log(L_\lambda)$ in this work. For the rest of the lens sample except HS2209, their broad line properties are adopted from the literature~\citep{Sluse2012, Peng2006} taking into account lensing magnification. For HS2209, the spectrum was observed at the Keck-II Telescope in September 2015. We derived the line properties from the spectrum using the same approach as~\citet{Sluse2012}, based on \Mgii.
The \mbh\ measurements, together with the properties of the broad-line, are listed in Table~\ref{mbh}. 
The uncertainty of the \mbh\ are estimated to be $0.4$~dex.
We note that the magnification correction for these systems are not fully self-consistent, in the sense that the magnification is slightly different for the host galaxy light and the black holes mass. This difference could  in principle introduce some systematics on the correlations. However, these errors are smaller than the calibration error on \mbh (0.4 dex), given that the virial relations depend on roughly the square root of the $\log(L_\lambda)$.

@@

\section{surface photometry inference}\label{sec:lens_model}
%
In this section, we describe how we derived surface photometry of the lensed galaxies taking lensing effects into account. Lens models of 4/8 systems, namely HE0435~\citep{Wong2017}, RXJ1131~\citep{Suyu2013}, WFI2033~\citep{Rusu2019} and SDSS1206~\citep{Birrer2019} have been published by the H0LiCOW project. The goal of those models was strong lens time-delay cosmography~\citep{Refsdal1966, Treu2016}, and the reconstruction of the host galaxy light (via pixellated distribution~\citep{Suy++06} or shapelets~\citep{Refregier2003}) was a byproduct. \citet{Ding2017b} used those reconstructions for two of the systems (HE0435 and RXJ1131), and then fitted a simply parametrized surface brightness profile to the reconstruction to measure the host properties as the non-lensed AGN case.
% mimic what is done in non-lensed AGN.

In this work, in order to reproduce more closely and uniformly what is
done in non-lensed AGN, we develop a strategy to obtain a one step
measurement of the host galaxy light described by a \sersic\ surface
brightness profile. For the 4/8 systems already studied by the H0LiCOW
project, we will make a comparison to characterize systematic
uncertainties related to the modelling techniques.

@@

We carry out a forward modelling process to simultaneously constrain the lens model, subtract the central AGN light, and infer the photometry of the host galaxy. For any extended objects, including the lensing galaxy and source galaxy, we assume their surface brightness can be described by the 2-D elliptical \sersic\ profile. We start with a single \sersic\ profile and consider to use two \sersic\ if any significant residual indicate multiple components. For a single \sersic\ profile, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical results\footnote{It has been shown in~\citet{Ding2017a} that choosing this prior for \sersic\ index $n$ yields unbiased host magnitude inferences.}. The bright nucleus is unresolved and modelled by a scaled point spread function (PSF) in the image plane. We also impose that the AGN and its host galaxy have the same center. Following standard practice that has been shown to produce good models \citep[e.g.,][and references therein]{Treu2010}, we adopt elliptical power-law density profiles to define the surface mass density of the deflector, with an external shear.

@@

In general, for one lens system with a number of $N$ initial PSF guesses, we perform in total $N\times12$ (i.e., $2$ by (ii) $\times~2$ by (iii) $\times~3$ by (iv)) fits. After all fits are completed, we rank their performance based on their best-fitted $\chi^2$ value. Since there is no evidence of a better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then combine their best-fit results based on the weighting algorithm introduced by D20. The degrees of freedom are the same for each of the model, ensuring that the weighting scheme is internally self-consistent. The weights are defined by:
\begin{eqnarray}
\label{eq:weights}
w_i = {\rm exp} \big(- \alpha \frac{ (\chi_i ^2 - \chi_{\rm best} ^2 )}{2 \chi_{\rm best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter\footnote{Defining $\alpha$ as the {\it inflation} parameter it is assumed that it is larger than ~$1$, so as to err on the side of caution and include more choices that would be allowed strictly by statistical noise considerations.} so that when $i=4$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=4} ^2 - \chi_{\rm best} ^2 }{2 \chi_{\rm best} ^2} = 2.
\end{eqnarray} 
Then, the results for {\it noise boost} and {\it PSF iteration} are combined equally to derive the value of host properties and the root-mean-square error (i.e., $\sigma$ level) based on the weights of the $4+4$ (i.e., {\it noise boost} and {\it PSF iteration}) options by:
\begin{eqnarray}
\label{eq:infer_value}
\bar{x}  =  \frac{  \sum_{i=1}^{N}   x_i * w_i  }{\Sigma w_i} ,
\end{eqnarray} 
\begin{eqnarray}
\label{eq:infer_scatter}
\sigma =   \sqrt{ \frac{  \sum_{i=1}^{N}   (x_i -  \bar{x} ) ^2 * w_i  }{\Sigma w_i} }.
\end{eqnarray}

@@

\subsection{Photometry Inference}\label{sec:photometry}
In this subsection, we describe the details of the fitting for each system and present the inference of the photometry of the host galaxy.

\subsubsection{HE0435}\label{subsec:HE0435}
We follow the approach described in the previous section. We select 5 isolated stars in this field as initial PSFs to input to the fitting, for a total of 60 fits. Based on the top-eight choices, we perform the weighting algorithm and measure the host flux, host-to-total flux ratio, effective radius and \sersic\ index. The inference results are shown in Table~\ref{tab:host_measure}, (2)$-$(6) columns.

\subsubsection{RXJ1131}
A lens model of RXJ1131 based on ACS/F814W data has been presented by~\citet{Suyu2013}. The host galaxy of this system is lensed to an extended arc. A clear bulge and disk component can be identified. Thus, we describe the host galaxy with two \sersic\ profiles with index values $n$ fixed to $1$ and $4$, respectively, to mimic the light distribution of the disk and bulge. In addition, following~\citet{Suyu2013}, we consider the perturbations by the small object ($0\farcs{5}$ in the north) and describe it as a SIS and \sersic\ for its mass and light, respectively.

\subsubsection{WFI2033}
WFI2033 is the last quadruply lensed system in our sample whose lens model has been previously investigated \citep{Rusu2019}. There is a satellite galaxy North of the lens. However, the satellite galaxy has much smaller mass than the main deflector. In addition, there is a galaxy west of the main target, which also has a small effect on the total macro-magnification $(<10\%)$. Thus, we ignore their influence on the magnification but only fit the light of the satellite galaxy using a \sersic\ model. 
We select a total of 8 initial PSF stars to model this system.

\subsubsection{SDSS1206}
SDSS1206 is a unique system -- the AGN is doubly imaged by the deflector while most of the host falls inside the inner caustic and ends up being quadruply imaged. Following~\citet{Birrer2019}, we consider the galaxy triplet group at the north-west and use a single SIS model to denote their overall mass perturbation. Moreover, as noted by~\citet{Birrer2019}, a sub-clump is located in the north which is hardly visible \citep[see Figure~1 in][]{Birrer2019}. We model this sub-clump as a SIS mass model and a circular \sersic\ light model with joint centroids. It is worth noting that we are using the same imaging modelling tool as~\citet{Birrer2019}.

Due to the limited number of stars in the field of view, there are only 2 stars available as initial PSF. To expand the volume of modelling options, we also take the stack of the two bright stars as derived by~\citet{Birrer2019}, as a third initial PSF. We find a visible residuals at the fitted lensed arcs region using a single \sersic\ model as host. However, a double \sersic\ model does not significantly improve the goodness of fit. Thus, we adopt the single \sersic\ model in our final inference. Our inferred results are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(d).

\subsubsection{HE1104}
HE1104 is a typical doubly imaged quasar. We have selected in total of 5 initial PSFs to perform the fit. There is an object at the northeast. However, since we do not know its redshift and considering it is further away from the lens we do not model it explicitly but just mask it out in the fitting.

\subsubsection{SDSS0246}
Having been imaged with WFC3-UVIS/F814W, the resolution of the data for this system (together with the remaining two systems) is much higher than for those imaged in the IR, with a drizzled pixel scale of $0\farcs{}03$. However, the arcs are much fainter compared with those of other systems imaged in the IR band. As a result, fewer pixels with signal are available for the fit than for other systems. Nevertheless, the host inference is successfully reconstructed as shown in Figure~\ref{fig:image_inference}-(f) and Table~\ref{tab:host_measure} (3 initial PSF guesses were adopted).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% my commands
\newcommand{\lcdm}{$\Lambda$CDM}
\newcommand{\hst}{{\it HST}}
\newcommand{\hc}{$H_0$}
\newcommand{\efr}{$R_{\mathrm{eff}}$}
\newcommand{\galfit}{{\sc Galfit}}
\newcommand{\mbh}{$\mathcal M_{\rm BH}$}
\newcommand{\lhost}{$L_{\rm host}$}
\newcommand{\mr}{$Mag_{\rm ~R}$}
\newcommand{\halpha}{H$_{\alpha}$}
\newcommand{\Hb}{H$_{\beta}$}
\newcommand{\sersic}{S\'ersic}
\newcommand{\lenstronomy}{{\sc Lenstronomy}}
\newcommand{\reff}{{$R_{\mathrm{eff}}$}}
\newcommand{\kmsMpc}{km~s$^{\rm -1}$~Mpc$^{\rm -1}$}
\newcommand{\kms}{\ifmmode{\,\rm{km}\, \rm{s}^{-1}}\else{$\,$km$\,$s$^{-1}$}\fi}
\newcommand{\sigstar}{{$\sigma_*$}}
\newcommand{\mstar}{{$M_*$}}
\newcommand{\Mgii}{Mg$_{\rm II}$}
\newcommand{\Civ}{C$_{\rm IV}$}
%\newcommand{\farcs}{\mbox{\ensuremath{.\!\!^{\prime\prime}}}}% fractional arcsecond symbol: 0.''0
\newcommand{\sam}{\texttt{SAM}}
\newcommand{\mbii}{\texttt{MBII}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
\newcommand{\todo}[1]{\textcolor{red}{[{\bf Todo}: #1]}}  
\newcommand{\red}[1]{{ \textcolor{red}{#1}}}
\newcommand{\blue}[1]{{\bf \textcolor{blue}{#1}}}
\newcommand{\pink}[1]{{\textcolor{magenta}{#1}}}

@@

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[X. Ding et al.]{
Xuheng Ding,$^{1}$\thanks{E-mail: dxh@astro.ucla.edu}
Tommaso Treu,$^{1}$
Simon Birrer,$^{2}$
Adriano Agnello,$^{3}$\newauthor
Dominique Sluse,$^{4}$
Chris Fassnacht,$^{5}$
Matthew W. Auger,$^{6}$
Kenneth C. Wong,$^{7}$ \newauthor
Sherry H. Suyu,$^{8,9,10}$
Takahiro Morishita,$^{11}$
Cristian E. Rusu,$^{12,13,14}$
Aymeric Galan,$^{15}$
\\
% List of institutions
$^{1}$Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{3}$European Southern Observatory, Karl-Schwarzschild-Strasse 2, 85748 Garching, Germany\\
$^{4}$STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium\\
$^{5}$Department of Physics, University of California, Davis, CA 95616, USA\\
$^{6}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
$^{7}$Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
$^{8}$Max-Planck-Institut f{\"u}r Astrophysik, Karl-Schwarzschild-Str.~1, 85748 Garching, Germany\\
$^{9}$Physik-Department, Technische Universit\"at M\"unchen, James-Franck-Stra\ss{}e~1, 85748 Garching, Germany\\
$^{10}$Academia Sinica Institute of Astronomy and Astrophysics (ASIAA), 11F of ASMAB, No.1, Section 4, Roosevelt Road, Taipei 10617, Taiwan\\
$^{11}$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA\\
$^{12}$National Astronomical Observatory of Japan, 2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan\\
$^{13}$Subaru Telescope, National Astronomical Observatory of Japan, 650 N Aohoku Pl, Hilo, HI 96720\\
$^{14}$Department of Physics, University of California, Davis, 1 Shields Avenue, Davis, CA 95616, USA\\
$^{15}$Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique 
F\'ed\'erale de Lausanne (EPFL), Observatoire de Sauverny, 1290 Versoix, 
Switzerland
}

@@

% Abstract of the paper
\begin{abstract}
One of the main challenges in using high redshift active galactic nuclei to study the correlations between the mass of the supermassive Black Hole (\mbh) and the properties of their active host galaxies is instrumental resolution. Strong lensing magnification effectively increases instrumental resolution and thus helps to address this challenge. In this work, we study eight strongly lensed active galactic nuclei (AGN) with deep {\it Hubble Space Telescope} (\hst) imaging, using the lens modelling code \lenstronomy\ to reconstruct the image of the source. Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on stellar population models.  \mbh\ are estimated from broad emission lines using standard methods. Our results are in good agreement with recent work based on non-lensed AGN, \blue{demonstrating the great potential of using strongly lensed AGNs to extend the study of the correlations to higher redshifts.}
At the moment, the sample size of lensed AGN is small and thus they provide mostly a consistency check on systematic errors related to resolution for the non-lensed AGN. However, the number of known lensed AGN is expected to increase dramatically in the next few years, through dedicated searches in ground and space based wide field surveys, and they may become a key diagnostic of black hole and galaxy co-evolution. 
\end{abstract}

@@

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
\section{Introduction}
The tight correlations between the masses (\mbh) of supermassive black holes (BHs) and their host galaxies properties including stellar mass (\mstar), stellar velocity dispersion ($\sigma_*$) and luminosity (\lhost), known as scaling relations, are usually considered as a result of their co-evolution ~\citep[e.g.,][]{Mag++98, F+M00, Geb++01b, M+H03, Gul++09,Beifi2012, H+R04, Gra++2011}. Cosmological simulations of structure formation are able to reproduce the local tight relation based on {\bf the} physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or having them share a common gas supply~\citep{Cen2015, Menci2016}. However, it has also been suggested that the correlations arise statistically, without any physical coupling, as a result of stochastic mergers~\citep{Peng2007, Jahnke2011, Hirschmann2010}.

@@

As the samples of AGN grow to increase statistical power, it is very important to make sure that systematics do not dominate the error budget. One of the main potential {\bf sources} of systematics is the finite resolution of \hst\ images. Even with modern techniques, AGN hosts remain barely resolved at \hst\ resolution, and therefore it would be very useful to verify the results at higher resolution. This is the goal of this work.

@@

The sample of lensed AGN is too limited in size to constrain evolution by itself. Therefore, we use it primarily to verify the results of D20.  The D20 sample includes 32 AGN measurements in the redshift range {\bf of} $1.2<z<1.9$. They also collected 59 intermediate redshift (i.e., $0.35<z\lesssim1.2$) AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 local (i.e., $z\lesssim0.007$) measurements~\citep{Bennert++2011, H+R04}. It is worth noting that they are so far the largest \hst\ imaging AGN sample with redshift range up to $z\sim1.9$.

@@

To ensure the consistency of \mbh\ estimates based on different broad lines, we adopt the following set of self-consistent recipes following D20:
\begin{eqnarray}
\label{recipe}
\log \left(\frac{\mathcal M_{\rm BH}}{M_{\odot}}\right)&~=~& a+b \log \left(\frac{ \rm L _{\lambda_{line}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2 \log \left(\frac{\rm FWHM(line)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}
where $\lambda_{\rm line}$ is the reference wavelength of the local continuum luminosities for different emission lines. The following values are adopted:
%
$a$\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
$b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
$\lambda_{\rm line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}~(\AA).
%
The broad line properties of our samples are adopted from the literature, with a few corrections/exceptions. % \citep{Sluse2012, Peng2006, Shen2011}.
The line properties of SDSS1206 have been inferred by~\citet{Shen2011}. However, this system was investigated as a non-lensed AGN and the lensing magnification on the intrinsic continuum luminosity was not considered. We follow~\citet{Birrer2019} and apply the same magnification correction on the $\log(L_\lambda)$ in this work. For the rest of the lens sample except HS2209, their broad line properties are adopted from the literature~\citep{Sluse2012, Peng2006} taking into account lensing magnification. For HS2209, the spectrum was observed at the Keck-II Telescope in September 2015. We derived the line properties from the spectrum using the same approach as~\citet{Sluse2012}, based on \Mgii.
The \mbh\ measurements, together with the properties of the broad-line, are listed in Table~\ref{mbh}. 
The uncertainty of the \mbh\ {\bf is} estimated to be $0.4$~dex.
We note that the magnification correction for these systems are not fully self-consistent, in the sense that the magnification is slightly different for the host galaxy light and the black holes mass. This difference could  in principle introduce some systematics on the correlations. However, these errors are smaller than the calibration error on \mbh (0.4 dex), given that the virial relations depend on roughly the square root of the $\log(L_\lambda)$.

@@

\section{surface photometry inference}\label{sec:lens_model}
%
In this section, we describe how we derived surface photometry of the lensed galaxies taking lensing effects into account. Lens models of 4/8 systems, namely HE0435~\citep{Wong2017}, RXJ1131~\citep{Suyu2013}, WFI2033~\citep{Rusu2019} and SDSS1206~\citep{Birrer2019} have been published by the H0LiCOW project. The goal of those models was strong lens time-delay cosmography~\citep{Refsdal1966, Treu2016}, and the reconstruction of the host galaxy light (via pixellated distribution~\citep{Suy++06} or shapelets~\citep{Refregier2003}) was a byproduct. \citet{Ding2017b} used those reconstructions for two of the systems (HE0435 and RXJ1131) and then fitted a simply parametrized surface brightness profile to the reconstruction to measure the host properties as the non-lensed AGN case.
% mimic what is done in non-lensed AGN.

In this work, in order to reproduce more closely and uniformly what is
done in non-lensed AGN, we develop a strategy to obtain a one-step
measurement of the host galaxy light described by a \sersic\ surface
brightness profile. For the 4/8 systems already studied by the H0LiCOW
project, we will make a comparison to characterize systematic
uncertainties related to the modelling techniques.

@@

We carry out a forward modelling process to simultaneously constrain the lens model, subtract the central AGN light, and infer the photometry of the host galaxy. For any extended objects, including the lensing galaxy and source galaxy, we assume their surface brightness can be described by the 2-D elliptical \sersic\ profile. We start with a single \sersic\ profile and consider {\bf using} two \sersic\ if any significant residual {\bf indicates} multiple components. For a single \sersic\ profile, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical results\footnote{It has been shown in~\citet{Ding2017a} that choosing this prior for \sersic\ index $n$ yields unbiased host magnitude inferences.}. The bright nucleus is unresolved and modelled by a scaled point spread function (PSF) in the image plane. We also impose that the AGN and its host galaxy have the same center. Following standard practice that has been shown to produce good models \citep[e.g.,][and references therein]{Treu2010}, we adopt elliptical power-law density profiles to define the surface mass density of the deflector, with an external shear.

@@

In general, for one lens system with a number of $N$ initial PSF guesses, we perform in total $N\times12$ (i.e., $2$ by (ii) $\times~2$ by (iii) $\times~3$ by (iv)) fits. After all fits are completed, we rank their performance based on their best-fitted $\chi^2$ value. Since there is no evidence of better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then {\bf combined} their best-fit results based on the weighting algorithm introduced by D20. The degrees of freedom are the same for each of the model, ensuring that the weighting scheme is internally self-consistent. The weights are defined by:
\begin{eqnarray}
\label{eq:weights}
w_i = {\rm exp} \big(- \alpha \frac{ (\chi_i ^2 - \chi_{\rm best} ^2 )}{2 \chi_{\rm best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter\footnote{Defining $\alpha$ as the {\it inflation} parameter it is assumed that it is larger than ~$1$, so as to err on the side of caution and include more choices that would be allowed strictly by statistical noise considerations.} so that when $i=4$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=4} ^2 - \chi_{\rm best} ^2 }{2 \chi_{\rm best} ^2} = 2.
\end{eqnarray} 
Then, the results for {\it noise boost} and {\it PSF iteration} are combined equally to derive the value of host properties and the root-mean-square error (i.e., $\sigma$ level) based on the weights of the $4+4$ (i.e., {\it noise boost} and {\it PSF iteration}) options by:
\begin{eqnarray}
\label{eq:infer_value}
\bar{x}  =  \frac{  \sum_{i=1}^{N}   x_i * w_i  }{\Sigma w_i} ,
\end{eqnarray} 
\begin{eqnarray}
\label{eq:infer_scatter}
\sigma =   \sqrt{ \frac{  \sum_{i=1}^{N}   (x_i -  \bar{x} ) ^2 * w_i  }{\Sigma w_i} }.
\end{eqnarray}

@@

\blue{The inferred photometry of the host galaxy for all the eight systems are listed in Table~\ref{tab:host_measure}, (2)$-$(6) columns. The detailed information of the fitting process for each system is in Appendix~\ref{sec:photometry}.}
